11th International Satisfiability Modulo Theories Competition (SMT-COMP 2016): Rules and Procedures

### 2017-04-19 rules/rules17.tex
Add draft of 2017 rules

For a given competition benchmark~$b$, let~$F_b \geq 1$ be the total
number of benchmarks in $b$'s benchmark family that were used in the
competition track to which the division belongs.  We define the weight
for benchmark~$b$ as $\alpha_b = (1 + \log_e F_b) / F_b$.\footnote{See
  Section~\ref{sec:competition-wide} for a motivating discussion of
  log scaling.}  We define the \emph{normalized weight} for
benchmark~$b$ as $\alpha'_b = \alpha_b / (\sum_{b'} \alpha_{b'})$,
where the sum is over all benchmarks in the division.

For main track and unsat-core track divisions, we will separately
compute the weighted sum of all raw scores
(Section~\ref{sec:benchmark-scoring}) $$\sum_b \alpha'_b \cdot \langle
e_b, n_b, w_b, c_b\rangle$$ where the sum is over all benchmarks in
the division to assess parallel performance, and the weighted sum of
all sequential scores (Section~\ref{sec:sequential}) to assess
sequential performance.  For application track divisions, division
scores will be based on raw scores only.\footnote{Since application
  track benchmarks may be partially solved, defining a useful
  sequential score for the application track would require information
  not provided by the raw score, e.g., detailed timing information for
  each result.}

>>>>

For a given competition benchmark~$b$, let~$F_b \geq 1$ be the total
number of benchmarks in $b$'s benchmark family that were used in the
competition track to which the division belongs.  We define the weight
for benchmark~$b$ as $\alpha_b = (1 + \log_e F_b) / F_b$.\footnote{See
  Section~\ref{sec:competition-wide} for a motivating discussion of
  log scaling.}  We define the \emph{normalized weight} for
benchmark~$b$ as $\alpha'_b = \alpha_b / (\sum_{b'} \alpha_{b'})$,
where the sum is over all benchmarks in the division.  Let~$N$ be the
total number of benchmarks in the division.

For main track and unsat-core track divisions, we will separately
compute the weighted sum of all raw scores
(Section~\ref{sec:benchmark-scoring}) $$\sum_b \alpha'_b \cdot \langle
e_b \cdot N, n_b \cdot N, w_b, c_b\rangle$$ where the sum is over all
benchmarks in the division to assess parallel performance, and the
weighted sum of all sequential scores (Section~\ref{sec:sequential})
to assess sequential performance.  For application track divisions,
division scores will be based on raw scores only.\footnote{Since
  application track benchmarks may be partially solved, defining a
  useful sequential score for the application track would require
  information not provided by the raw score, e.g., detailed timing
  information for each result.}
